Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-09-15 manuscript.tex
knit manuscript

We used R (Version 4.2.0; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.4; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.9; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{jsonlite} (Version 1.8.0; Ooms, 2014), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.4.1; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.2; Wickham \& Hester, 2020), \emph{shiny} (Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.

@@

Thus, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50\%. This slightly improved the fits of the sigmoids (Attractiveness: R\textsuperscript{2} = 0.79; Roundness: R\textsuperscript{2} = 0.60). However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.36). Descriptively, the results do not look substantially different (Fig. \ref{fig:groupEMainrev}).

>>>>

We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.0; Singmann, Bolker, Westfall, Aust, \& Ben-Shachar, 2021), \emph{broom.mixed} (Version 0.2.9.3; Bolker \& Robinson, 2020), \emph{dplyr} (Version 1.0.7; Wickham, François, Henry, \& Müller, 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{jsonlite} (Version 1.7.2; Ooms, 2014), \emph{lme4} (Version 1.1.27.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{Matrix} (Version 1.3.4; Bates \& Maechler, 2021), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{readr} (Version 2.1.1; Wickham \& Hester, 2020), \emph{shiny} (Version 1.7.1; Chang et al., 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.2.0; Wickham, 2021b), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.

@@

Thus, we re-analyzed the data, removing the participants whose calibration accuracy was not greater than 50\%. This slightly improved the fits of the sigmoids (Attractiveness: R\textsuperscript{2} = 0.79; Roundness: R\textsuperscript{2} = 0.60). However, the difference between sigmoids remained non-significant using the Kolmogorov-Smirnov test (D = 0.22, p = 0.35). Descriptively, the results do not look substantially different (Fig. \ref{fig:groupEMainrev}).
